% A workaround to allow relative paths in included subfiles
% that are to be compiled separately
% See https://tex.stackexchange.com/questions/153312/subfiles-inside-a-subfile-using-relative-paths
\providecommand{\main}{..}
\documentclass[\main/thesis.tex]{subfiles}

\begin{document}

% environment for acknowledgements.
\begin{acknowledgements}

I have been very fortunate to have met and worked with many brilliant and encouraging mentors, friends, and colleagues. I wish I could thank all those who made the journey to get a Ph.D. possible and (mostly) enjoyable, but then this section would be longer than the following thesis.

First, my two co-supervisors Martha White and Adam White are more than I could have asked for as mentors and friends. Meeting them at Indiana University - Bloomington will always be one of the most impactful moments in my life. I will always be grateful to have been part of their labs and could not see myself finishing my degree without their support and encouragement. I have been amazed at the passion and drive they put into their research and hope to emulate them as I progress in my career. Along with my supervisors, I am deeply grateful to my committee---Michael Bowling, Matthew Guzdial, and Andr\'{e} Barreto--- for engaging with my research and providing valuable feedback. Finally, I want to thank all the collaborators of the work presented in this thesis: Andrew Jacobsen, Andy Patterson, Zaheer Abbas, Wesley Chung, Daniel Graves, Jian Qian, and Volodymyr Tkachuk. Your contributions have made this thesis significantly better. I look forward to working together in the future and continuing to be colleagues and friends.

I am deeply grateful for the support and friendship of my fellow students and colleagues. Special appreciation goes to Alex Kearney for the continued support, friendship, and smart-witty banter that made the hard times fly by. There is always time for (gluten-free) pasta, especially at 1 a.m. in Toronto. I also want to thank Andrew Jacobsen for his consistent stream of challenging music suggestions, his eccentric and exciting behavior at drinks, and his friendship through the years. I want to thank Shibhansh Dohare for getting me deeply embedded in the climbing world and making exercise in the last few years of my Ph.D. enjoyable. Also, thank you to Eric Graves for being a great introduction to the department and for having long discussions about tea, life, and research as we made tea for TTTs. I want to acknowledge Marlos Machado and Craig Sherston for being role models as senior Ph.D. students. I especially want to thank Marlos for the early morning conversations and advice in the first year of my degree. I also want to acknowledge Johannes G\"unther for his friendship and mentorship in doing research and finding my voice as a person and researcher. Many thanks also to Andy Patterson and Cam Linke (along with AJ) for the many fun conversations and drinks throughout the years, Roshan Shariff for his wisdom and engaging discourse on anything in mathematics, Raksha Kumaraswamy for being the best desk neighbor both here and at Indiana University, and Yangchen Pan for his mentorship and encouragement in my first research project. I want to send my appreciation and thanks to J. Fernando Hernandez Garcia, Abhishek Naik, Niko Yasui, Dylan Brenneis, Andy Wong, Brian Tanner, James Bell, Khurram Javed, Banafsheh Rafiee, Kirby Banman, Alex Lewandowski, and Chunlok Lo.
  
Finally, I want to thank my family and friends (those outside the department) for supporting me through these tumultuous years. My Mom and Dad for being my biggest supporters and advocates; Sarah Nagelvoort for being not only a sister but a friend, mentor, and listening post; Mark Nagelvoort for being the best brother-in-law ever; Henry and Evelyn Nagelvoort for letting me play with their toys when I'm in Bloomington; Roshni Sajiv Kumar for her support and partnership, I am grateful for your compassion and patience as I was preparing for my defense; Dan Kenneally, Pat Miller, and Ed Cowie for being great friends for an uncountable number of years and always being available to have wild conversations about AI's takeover of the world; and finally, Jonathan Song for his help in a difficult time.

My work was made possible by the generous support of IVADO, and the Alberta Machine Intelligence Institute (Amii). The computing resources used for this research were provided by Compute Canada (now Digital Research Alliance of Canada).

\end{acknowledgements}

\end{document}